UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio and Reconfigurable Intelligent Surface

### 2022-08-13 main.tex
:pencil: Update scattering principles

	\emph{Notations:}
	Italic, bold lower-case, and bold upper-case letters denote scalars, vectors and matrices, respectively.
	$\boldsymbol{0}$ and $\boldsymbol{1}$ denote zero and one array of appropriate size, respectively.
	$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote the real nonnegative and complex spaces of dimension $x \times y$, respectively.
	$j$ denotes the imaginary unit.
	$\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote the argument, rank, trace, a square matrix with input vector on main diagonal, and a vector retrieving main diagonal of input square matrix, respectively.
	$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $\lvert{\cdot}\rvert$, and $\lVert{\cdot}\rVert$ denote the conjugate, transpose, conjugate transpose, absolute value, and Euclidean norm operators, respectively.
	$(\cdot)^{(r)}$ and $(\cdot)^{\star}$ denote the $r$-th iterated and terminal solutions, respectively.
	The distribution of a \gls{cscg} random variable with zero mean and variance $\sigma^2$ is denoted by $\mathcal{CN}(0,\sigma^2)$, and $\sim$ means ``distributed as''.
\end{section}

% \begin{section}{Scattering/Reflecting Principles}

@@

			% For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.
			% To support the operation of on-chip components, the majority of incident wave is consumed for energy harvesting
			% According to \cite{Hansen1989}, the reradiated part can be decomposed into \emph{structural} component that consistently contributes to the environment multipath, and \emph{antenna} component that depends on the antenna-load impedance mismatch.

@@

			% Antenna-based scatterers are typically considered in \gls{bc} and \gls{sr} literatures, while some \gls{ris}
			% BC and SR typically antenna-based, RIS both

@@

			% The core concept of metamaterials is to produce materi- als by using artificially designed and fabricated structural units made of metallic or dielectric materials to achieve the desired properties and functionalities. These subwave- length structural units—the constituent artificial “atoms” and “molecules” of the metamaterial—can be tailored in shape and size.

			% The lattice constant and interatomic inter- action can be artificially tuned. They can be designed and placed at desired locations. By engineering the arrange- ment of these small unit cells into the desired architecture or geometry, one can tune the effective permittivity or permeability of the metamaterial to positive, near-zero, or negative values. Thus, metamaterials can be endowed with properties and functionalities unattainable in natural materials [11], [12].

			% 2) Epsilon-negative (ENG) materials: They display a neg- ative permittivity ε but positive permeability μ. ENG could be formed using conducting rods (thin wires). In this case, the refractive index becomes imaginary, and EM waves cannot propagate in the material but are reflected at the boundary between air and the medium. Any propagation into the medium would be evanescent. 3) Mu-negative (MNG) materials: They have a positive ε but negative μ. MNG and could be formed using split-ring resonators (SRRs). Again, in this case, the refractive index becomes imaginary, and EM waves cannot propagate in the material and will be reflected at the boundary between air and the material.

			% The metamaterials, in general, are composite materials. Each unit cell (SRR or other designs) has an individually tailored response to the EM field. This is similar to how light interacts with everyday materials; materials such as glass or lenses are made of atoms. An averaging or macroscopic effect is produced. The cell of a metamaterial is designed to mimic the EM response of atoms, only on a much larger scale. Also, as part of periodic com- posite structures, these are designed to have a stronger EM coupling than that found in nature. The larger scale allows for more control over the EM response, while each unit is smaller than the wavelength of the radiated EM wave. Achieving fascinating functionalities of metamaterials typically entails multiple stacks of material layers, which not only leads to extensive loss but also brings a lot of challenges in fabrication. Many metamaterials consist of complex metallic wires and other structures that require sophisticated fabrication technology and are difficult to assemble. 3-D metamaterials can be extended by arranging electrically small scatters or holes into a 2-D pattern at a surface or interface. This surface version of a metamaterial has been given the name metasurface. For many applica- tions, metasurfaces can be used in place of metamaterials. They have the advantage of taking up less physical space than full 3-D metamaterial structures do; consequently, they offer the possibility of less-lossy structures as well.

			% In metamaterial-based RIS, the equivalent impedance depends on various factors related to the design of the metamaterial unit. Therefore, there exist several meth- ods to change the equivalent impedances and, thus, the reconfigurable reflection coefficients. The first one is to use functional materials, such as graphene [73] and liquid crystals [74], [75], whose relative permittivity can be var- ied with the applied voltage. The second one is to change the physical structure of the metamaterial unit, such as the physical dimension or orientation of the unit [76], [77]. The third one is to vary the external biasing voltage applied on the tunable electronic devices, such as p-i-n diodes and varactor diodes [72], [78]–[82].

			% Metamaterial consists of numerous sub-wavelength structural units made of metallic or dielectric materials.
			A typical metamaterial-based scatterer consists of multiple material layers and a smart controller \cite{Wu2020}.
			The outer metamaterial layer involves numerous sub-wavelength structural units made of metallic or dielectric materials.
			% The shape and size of each unit cell can be artificially altered for customized response to the electromagnetic field.
			% One can change the effective permittivity or permeability of the metamaterial by manipulating the lattice constant and inter-atomic interaction \cite{Zhou2021}.
			The properties of unit cells can be artificially tuned for unconventional effective permittivity $\epsilon$ and permeability $\mu$, producing customizable response to the electromagnetic field \cite{Zhou2021}.
			Using epsilon-negative material (e.g., conducing rods) or mu-negative material (e.g., split-ring resonators), ideal metamaterial-based scatterers can reflect the incident waves at the boundary between free space and metamaterial without receiving them \cite{Huang2021a}.
			This mainly applies a phase shift on the reflected wave and any propagation into the metamaterial would be evanescent.
			% It mainly applies a phase shift on the reflected wave, while any propagation into the metamaterial would be evanescent.
			% The reflection happens at the boundary between free space and metamaterial, which mainly applies a phase shift on the reflected wave.
			% There exists several methods to change the equivalent impedance of metamaterial unit, such as
			% applied voltage on
			% functional materials, such as graphene [73] and liquid crystals [74], [75]
			Depending on the type of metamaterial, its equivalent impedance can be controlled by voltage (for functional materials \cite{Singh2020} and tunable diodes \cite{Costa2021}) or architecture (for resonant elements \cite{Bialkowski2008}).
			For metamaterial-based scatterers with a discrete impedance set, the reflection coefficient at metamaterial state $m$ is
			\begin{equation}
				\Gamma_m = \frac{Z_m - Z_0}{Z_m + Z_0},
			\end{equation}
			where $Z_m$ is the equivalent impedance of metamaterial unit at state $m$ and $Z_0 = \qty{377}{\ohm}$ is the characteristic impedance of free space.
		\end{subsubsection}
		% TODO discuss how BC, SR, RIS relates to both: BC and SR typically antenna-based, RIS both
	\end{subsection}

	Passive backscatter nodes harvest energy from and modulate information over surrounding \gls{rf} signals.
	As shown in Fig. \subref*{fi:block_diagram}, a typical passive node consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
	Its equivalent circuit is presented in Fig. \subref*{fi:equivalent_circuit}.
	% When illuminated, the node absorbs a portion of the impinging wave for information decoding and energy harvesting \cite{Kim2021a}, while scatters the remaining back to the space. The scattered signal is further decomposed into the \emph{structural} component that consistently contributes to environment multipath and covered by channel estimation \cite{Boyer2014}, and the
	When illuminated, the node absorbs a portion of the impinging wave for information decoding and/or energy harvesting \cite{Kim2021a}, and backscatters the remaining as \emph{structural} and \emph{antenna} components.
	% The scattered signal is further decomposed into the \emph{structural} component that consistently contributes to environment multipath and covered by channel estimation \cite{Boyer2014}, and the \emph{antenna} mode component that
	% and \emph{antenna} mode components \cite{Hansen1989}.
	The former consistently contributes to environment multipath and can be modelled by channel estimation \cite{Boyer2014}, while the latter depends on antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
	% Depending on structure, shape and material of general objects, structural scattering consistently contributes to environment multipath and is covered by channel estimation \cite{Boyer2014}.
	% In contrast, antenna scattering models radiation pattern from antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
	Fig. \subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ states, where the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as%
	% \footnote{It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.}
	% \begin{equation}
	% 	\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
	% 	\label{eq:reflection_coefficient}
	% \end{equation}
	where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.

	\begin{subsection}{BackCom/SR: Backscatter Modulation}
		% Backscatter sources encode self message by \emph{randomly changing reflection states.} For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding complex constellation point $c_m$ by \cite{Thomas2012a}
		Backscatter sources encode self message by \emph{random reflection states variation.} For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by \cite{Thomas2012a}
		\begin{equation}
			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
			\label{eq:backscatter_modulation}
		\end{equation}
		where $0 \le \alpha \le 1$ is the amplitude scattering ratio that controls the harvest-scatter tradeoff at the direction of interest.
		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
		% ! Use larger alpha in simulation: for high-order QAM, some constellation point may harvests more power than others

@@

	\begin{subsection}{RIS: Channel Reconfiguration}
		% \gls{ris} elements assist legacy transmission by \emph{deterministically choosing phase shifts} based on relevant \gls{csi}. For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding phase shift $\theta_m$ by \cite{Wu2018}
		\gls{ris} elements assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
		For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ relates to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
		\begin{equation}
			\Gamma_m = \beta_m \exp(j \theta_m),
		\end{equation}
		where $0 \le \beta_m \le 1$ is overall amplitude scattering ratio of state $m$.
		% Based on relevant \gls{csi}
	\end{subsection}
	% Tags periodically switch between different states to perform backscatter modulation.
	% For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
	% \begin{equation}
	% 	\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
	% 	\label{eq:backscatter_modulation}
	% \end{equation}
	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
	% For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.

	\begin{subsection}{UniScatter: Bridge and Generalization}
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
			\\
			\subfloat[Time Block]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_block.tex}
				Input probability distribution and time block structure of \gls{sr}, \gls{ris}, and UniScatter.
				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
				Within channel coherence time, UniScatter nodes semi-randomly select reflection state for each backscatter block, with guidance from input probability distribution.
			\label{fi:uniscatter}
		% ? For a passive node with finite states, is it possible to unify backscatter modulation and channel reconfiguration by proper selection of reflection coefficient?
		UniScatter nodes simultaneously transmit and assist by \emph{adaptive input distribution design} based on primary and (cascaded) backscatter \gls{csi}.
		% The reflection pattern is neither fully random nor fully deterministic, but flexibly distributed to balance backscatter encoding and passive beamforming.
		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter semi-randomly selects reflection state for each backscatter block with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.} In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming. \gls{sr} and \gls{ris} can be regarded as extreme cases of UniScatter, where node input distribution boils down to uniform and deterministically biased, respectively.
		Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter nodes semi-randomly select reflection state for each backscatter block, with \emph{guidance of input probability $P(\Gamma_m)$} for state $m$. In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
		% \gls{sr} and \gls{ris} can be regarded as extreme cases of UniScatter nodes, where node input distribution boils down to uniform and deterministic, respectively.
		% flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
		% UniScatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
		% % Based on \gls{csi}, UniScatter adapts the reflection state distribution to unify data transmission and channel reconfiguration.
		% \gls{sr} and \gls{ris} can be regarded as its extreme cases, where node input distribution boils down to uniform and deterministically biased, respectively.
		% Within channel coherence time, UniScatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
		\begin{remark}
			Compared to conventional \gls{ris} literatures that optimize phase shifts under unit-module constraint, UniScatter nodes start from predefined reflection coefficients and designs their input distribution under sum-probability constraint to achieve flexible primary-backscatter tradeoff.
		\end{remark}
		% Next, we will discuss the input design in a UniScatter-enabled network.
		% consider a UniScatter-aided system to evaluate

@@

\end{section}

\begin{section}{UniScatter-Enabled Network}
	\begin{subsection}{System Model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.8\columnwidth}
			\footnotesize{
				\import{assets/illustration/}{uniscatter_network.eps_tex}
			}
			\caption{A UniScatter-enabled single-user multi-node network.}
			\label{fi:uniscatter_network}
		\end{figure}
		% As shown in Fig. \ref{fi:uniscatter_network}, we propose a UniScatter-enabled single-user multi-node network where the spectrum, energy and infrastructures are shared by two coexisting systems.
		% UniScatter-enabled single-user multi-node \gls{miso} network where multiple UniScatter nodes ride over a point-to-point transmission to
		As shown in Fig. \ref{fi:uniscatter_network}, we propose a UniScatter-enabled single-user multi-node \gls{miso} network where two coexisting systems share spectrum, energy and infrastructures.
		% In the primary point-to-point system, the \gls{ap} transmits information to the single-antenna user.
		% In the primary point-to-point system, a $Q$-antenna \gls{ap} transmit to a single-antenna user while assisted by $K$ nearby single-antenna UniScatters.
		The primary point-to-point transmission from a $Q$-antenna \gls{ap} to a single-antenna user is assisted by $K$ nearby single-antenna UniScatter nodes.
		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, $K$ nearby single-antenna UniScatter nodes modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
		For simplicity, we consider a quasi-static block fading model where channels remain constant within coherence interval while vary independently between consecutive blocks.
		% Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol period is $N \in \mathbb{Z}_{++}$ times the primary symbol period.
		Due to physical constraints on load switching, we assume the backscatter symbol period is $N \gg 1$ times longer than primary and consider integer $N$ without loss of generality.
		We also assume the direct channel and all cascaded channels can be estimated and fed back to the \gls{ap}.%
		\footnote{
			Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging.
			One possibility is the \gls{ap} sends training pilots, the tags respond in predefined manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.
		}
		Besides, we omit the signal reflected by two or more times\cite{Wu2019} and ignore the time difference of arrival from different paths\cite{Guo2019b}.

>>>>

	\emph{Notations:}
	Italic, bold lower-case, and bold upper-case letters denote scalars, vectors and matrices, respectively.
	$\boldsymbol{0}$ and $\boldsymbol{1}$ denote zero and one array of appropriate size, respectively.
	$\mathbb{R}_+^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote the real nonnegative and complex spaces of dimension $x \times y$, respectively.
	$j$ denotes the imaginary unit.
	% $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote the argument, rank, trace, a square matrix with input vector on main diagonal, and a vector retrieving main diagonal of input square matrix, respectively.
	$\mathrm{diag}(\cdot)$ returns a square matrix with the input vector on main diagonal.
	$(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $\lvert{\cdot}\rvert$, and $\lVert{\cdot}\rVert$ denote the conjugate, transpose, conjugate transpose, absolute value, and Euclidean norm operators, respectively.
	$(\cdot)^{(r)}$ and $(\cdot)^{\star}$ denote the $r$-th iterated and terminal solutions, respectively.
	The distribution of a \gls{cscg} random variable with zero mean and variance $\sigma^2$ is denoted by $\mathcal{CN}(0,\sigma^2)$, and $\sim$ means ``distributed as''.
\end{section}

@@

@@

@@

			A typical metamaterial-based scatterer consists of multiple material layers and a smart controller \cite{Wu2020}.
			The outer metamaterial layer involves numerous sub-wavelength structural units made of metallic or dielectric materials.
			The properties of unit cells can be artificially tuned for unconventional effective permittivity $\epsilon$ and permeability $\mu$, producing customizable response to the electromagnetic field \cite{Zhou2021}.
			Using epsilon-negative material (e.g., conducing rods) or mu-negative material (e.g., split-ring resonators), ideal metamaterial-based scatterers can reflect the incident waves at the boundary between free space and metamaterial without receiving them \cite{Huang2021a}.
			This mainly applies a phase shift on the reflected wave and any propagation into the metamaterial would be evanescent.
			Depending on the type of metamaterial, its equivalent impedance can be controlled by voltage (for functional materials \cite{Singh2020} and tunable diodes \cite{Costa2021}) or architecture (for resonant elements \cite{Bialkowski2008}).
			For metamaterial-based scatterers with a discrete impedance set, the reflection coefficient at metamaterial state $m$ is
				\Gamma_m = \frac{Z_m - Z_0}{Z_m + Z_0},
			where $Z_m$ is the equivalent impedance of metamaterial unit at state $m$ and $Z_0 = \qty{377}{\ohm}$ is the characteristic impedance of free space.

@@

	\begin{subsection}{BackCom/SR: Backscatter Modulation}
		\gls{bc} and \gls{sr} commonly employ antenna-based scatterers as backscatter information sources.
		% Backscatter information sources of \gls{bc} and \gls{sr} encode self message by \emph{random reflection states variation.}
		For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by \cite{Thomas2012a}
		\begin{equation}
			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
			\label{eq:backscatter_modulation}
		\end{equation}
		where $0 \le \alpha \le 1$ is the amplitude scattering ratio at the direction of interest.
		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
		% ! Use larger alpha in simulation: for high-order QAM, some constellation point may harvests more power than others
		% TODO by switching between reflection states, backscatter modulation introduces uncertainty.

@@

	\begin{subsection}{RIS: Channel Reconfiguration}
		% \gls{ris} elements assist legacy transmission by \emph{deterministically choosing phase shifts} based on relevant \gls{csi}. For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding phase shift $\theta_m$ by \cite{Wu2018}
		% \gls{ris} involves numerous
		\gls{ris} involves either a planar scattering antenna array or a metasurface of numerous metamaterial units.
		% Reflecting elements of \gls{ris} assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
		For each unit with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
		\begin{equation}
			\Gamma_m = \beta_m \exp(j \theta_m),
		\end{equation}
		where $0 \le \beta_m \le 1$ is the overall amplitude scattering ratio of state $m$.
		% Based on relevant \gls{csi}
	\end{subsection}
	% Tags periodically switch between different states to perform backscatter modulation.
	% For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
	% \begin{equation}
	% 	\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
	% 	\label{eq:backscatter_modulation}
	% \end{equation}
	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
	% For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.

	\begin{subsection}{UniScatter: Bridge and Generalization}
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
			}
			\\
			\subfloat[Time Block]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_block.tex}
				}
			}
			\caption{
				Input probability distribution and time block structure of \gls{sr}, \gls{ris}, and UniScatter.
				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
				Within channel coherence time, UniScatter nodes semi-randomly select reflection state for each backscatter block, with guidance from input probability distribution.
			}
			\label{fi:uniscatter}
		\end{figure}
		% ! Passive backscatter nodes harvest energy from and modulate information over surrounding \gls{rf} signals.
		% As shown in Fig. \subref*{fi:block_diagram}, a typical passive node consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
		% Its equivalent circuit is presented in Fig. \subref*{fi:equivalent_circuit}.
		% When illuminated, the node absorbs a portion of the impinging wave for information decoding and/or energy harvesting \cite{Kim2021a}, and backscatters the remaining as \emph{structural} and \emph{antenna} components.
		% The former consistently contributes to environment multipath and can be modelled by channel estimation \cite{Boyer2014}, while the latter depends on antenna-load impedance mismatch and can be used for backscatter modulation \cite{Boyer2012} and/or channel reconfiguration \cite{Wu2021b}.
		% Fig. \subref*{fi:scatter_model} illustrates the scatter model of a node with $M$ states.

		% ? For a passive node with finite states, is it possible to unify backscatter modulation and channel reconfiguration by proper selection of reflection coefficient?
		UniScatter nodes simultaneously transmit and assist by \emph{adaptive input distribution design} based on primary and (cascaded) backscatter \gls{csi}.
		% The reflection pattern is neither fully random nor fully deterministic, but flexibly distributed to balance backscatter encoding and passive beamforming.
		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter semi-randomly selects reflection state for each backscatter block with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.} In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming. \gls{sr} and \gls{ris} can be regarded as extreme cases of UniScatter, where node input distribution boils down to uniform and deterministically biased, respectively.
		Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter nodes semi-randomly select reflection state for each backscatter block, with \emph{guidance of input probability $P(\Gamma_m)$} for state $m$. In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
		% \gls{sr} and \gls{ris} can be regarded as extreme cases of UniScatter nodes, where node input distribution boils down to uniform and deterministic, respectively.
		% flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
		% UniScatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
		% % Based on \gls{csi}, UniScatter adapts the reflection state distribution to unify data transmission and channel reconfiguration.
		% \gls{sr} and \gls{ris} can be regarded as its extreme cases, where node input distribution boils down to uniform and deterministically biased, respectively.
		% Within channel coherence time, UniScatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
		\begin{remark}
			Compared to conventional \gls{ris} literatures that optimize phase shifts under unit-module constraint, UniScatter nodes start from predefined reflection coefficients and designs their input distribution under sum-probability constraint to achieve flexible primary-backscatter tradeoff.
		\end{remark}
		% Next, we will discuss the input design in a UniScatter-enabled network.
		% consider a UniScatter-aided system to evaluate
	\end{subsection}
\end{section}

\begin{section}{UniScatter}
	\begin{subsection}{System Model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.8\columnwidth}
			\footnotesize{
				\import{assets/illustration/}{uniscatter_network.eps_tex}
			}
			\caption{A UniScatter-enabled single-user multi-node network.}
			\label{fi:uniscatter_network}
		\end{figure}
		% As shown in Fig. \ref{fi:uniscatter_network}, we propose a UniScatter-enabled single-user multi-node network where the spectrum, energy and infrastructures are shared by two coexisting systems.
		% UniScatter-enabled single-user multi-node \gls{miso} network where multiple UniScatter nodes ride over a point-to-point transmission to
		As shown in Fig. \ref{fi:uniscatter_network}, we propose a UniScatter-enabled single-user multi-node \gls{miso} network where two coexisting systems share spectrum, energy and infrastructures.
		% In the primary point-to-point system, the \gls{ap} transmits information to the single-antenna user.
		% In the primary point-to-point system, a $Q$-antenna \gls{ap} transmit to a single-antenna user while assisted by $K$ nearby single-antenna UniScatters.
		The primary point-to-point transmission from a $Q$-antenna \gls{ap} to a single-antenna user is assisted by $K$ nearby single-antenna UniScatter nodes.
		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, $K$ nearby single-antenna UniScatter nodes modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
		For simplicity, we consider a quasi-static block fading model where channels remain constant within coherence interval while vary independently between consecutive blocks.
		% Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol period is $N \in \mathbb{Z}_{++}$ times the primary symbol period.
		Due to physical constraints on load switching, we assume the backscatter symbol period is $N \gg 1$ times longer than primary and consider integer $N$ without loss of generality.
		We also assume the direct channel and all cascaded channels can be estimated and fed back to the \gls{ap}.%
		\footnote{
			Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging.
			One possibility is the \gls{ap} sends training pilots, the tags respond in predefined manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.
		}
		Besides, we omit the signal reflected by two or more times\cite{Wu2019} and ignore the time difference of arrival from different paths\cite{Guo2019b}.
